\section{Current Status of \xxx and \yyy} \label{sec:status}
We have studied state-of-the-art consensus protocols and summarized 
three main issues of them on providing efficient fault tolerance to 
general server programs. Based on our analysis, we proposed \xxx, an RDMA-based 
\paxos system that can efficiently replicate unmodified server programs.
By integrating \xxx into VM, we proposed a novel Virtualized \smr 
system \yyy that makes VM fault-tolerance faster, more scalable, and 
more robust.

So far, we have come up with a complete system design of \xxx, including the 
normal case, leader election, and failure recovery protocol. We have 
implemented the normal case protocol of \xxx (\S\ref{sec:normal}) and collected 
initial evaluation results (\S\ref{sec:evaluation}). Our initial results show 
that compared with \nprog server programs' unreplicated executions, \xxx 
incurred \latencyoverhead overhead in response time and \tputoverhead in 
throughput. Its consensus latency outperformed four traditional consensus 
protocols by at least \comptradlow and faster than a recent RDMA-based 
consensus protocol \dare by \fasterDARE in average. This consensus latency 
stayed almost constant to the number of replicas and concurrent requests.
We will continue to implement the failure handling protocols (\ie, leader 
election and failure recovery) and test the performance and robustness. 
Besides, we will finish the development of several optimization mechanisms like 
transparent replication. An academic paper on \xxx has already been published 
at ACM Symposium on Cloud Computing 2017 (SoCC 2017).

Until now, we have brought up with a complete system design of \yyy and 
proposed several optimizations for improving the performance 
(\S\ref{sec:vm-integration}). For implementation, we have integrated 
\xxx into \kvm QEMU and finished developing the normal synchronization protocol 
and collected initial evaluation results. Our initial results show that \yyy's 
throughput is \avgtput higher than two popular VM fault-tolerance systems on 
4-vCPU VMs, \avgsixteen higher on 16-vCPU VMs. Meanwhile, \yyy consumes 
\avgbandwidth less network bandwidth than both of them on average.
We will continue to implement the failure handling protocol and measure the 
performance of our optimization techniques. We have published an academic paper 
about a novel disk replication design in \yyy at 23th IEEE International 
Conference on Parallel and Distributed Systems (ICPADS 2017).